### 2018-11-06 Sections/collision_handling_and_classical_errors.tex
No cloning proof

Alternately, Alice might be a part of a distributed computation, where she didn't prepare the data in the first place. In this instance, the no-cloning theorem implies that she cannot, in general, learn what the quantum state was, and therefore would be unable to make a second transmission attempt.

>>>>

Alternately, Alice might be a part of a distributed computation, where she didn't prepare the data in the first place. In this instance, the no-cloning theorem\index{No-cloning theorem}\footnote{The no-cloning theorem states that it is impossible to take a completely unknown quantum state and prepare an identical copy of it. That is, there is no quantum process\index{Quantum processes} implementing the map \mbox{$\mathcal{E}(\hat\rho\otimes\ket{0}\bra{0}) \to \hat\rho\otimes\hat\rho$} for unknown $\hat\rho$. Note that this result applies when $\hat\rho$ is arbitrary and unknown, but in general needn't apply if restricted to a particular basis, subject to other constraints, or we have \textit{a priori} knowledge of the state. \textit{Proof}:\index{No-cloning theorem!Proof} To see this, consider the evolution \mbox{$\hat{U}\ket\psi\ket{e} = e^{i\alpha(\psi,e)}\ket\psi\ket\psi$}, for some normalised ancillary state $\ket{e}$, where $\alpha$ denotes an irrelevant global phase factor. We have \mbox{$\langle\psi|\phi\rangle\langle e|e\rangle = \bra\psi\bra{e}\hat{U}^\dag\hat{U}\ket{\phi}\ket{e} = e^{-i[\alpha(\psi,e)-\alpha(\phi,e)]} \langle\psi|\phi\rangle^2$}. Since $\ket{e}$ is normalised, this implies \mbox{$|\langle\psi|\phi\rangle| = |\langle\psi|\phi\rangle|^2$}, which can only be true if \mbox{$ |\langle\psi|\phi\rangle|=0$} or \mbox{$ |\langle\psi|\phi\rangle|=1$}, which does not hold in general for arbitrary states $\ket\psi$ and $\ket\phi$. However, clearly if $\ket\psi$ and $\ket\phi$ are restricted to being equal or orthogonal then this constraint can be satisfied with an appropriate choice of $\hat{U}$.} implies that she cannot, in general, learn what the quantum state was, and therefore would be unable to make a second transmission attempt.

### 2018-11-06 Sections/interconnecting_and_interfacing_quantum_networks.tex
Adding image cropping
No cloning proof

For example, the cost metrics and attributes employed at the intercontinental level would most certainly be very different to those in a small LAN. A small LAN might be running applications whereby they can easily reproduce packets and thereby tolerate packet loss. But for a warehouse-scale commercial quantum computing enterprise, responsible for performing one stage of a distributed quantum computation, the loss of a single packet could be extremely costly, requiring the entire computation to be performed completely from scratch due to no-cloning and no-measurement limitations, something that may not come cheaply.

@@

\begin{figure}[!htbp]
\includegraphics[width=0.3\textwidth]{opt_inter}
\captionspacefig \caption{Light-matter interfacing between a single-photon state ($\hat{a}$, $\hat{a}^\dag$) and a two-level matter qubit ($\ket{g}$, $\ket{e}$). The absorption (emission) of a photon is associated with the excitation (relaxation) of the matter qubit ($\hat\sigma^\pm$).} \label{fig:opt_int}
\end{figure}

@@

\begin{figure}[!htbp]
\includegraphics[width=0.225\textwidth]{lambda_atom}
\captionspacefig \caption{Light-matter interfacing between an optical mode and a $\lambda$-configuration system. The two degenerate ground states represent the logical qubit (\mbox{$\ket{0}_L\equiv\ket{\!\uparrow}$}, \mbox{$\ket{1}_L\equiv\ket{\!\downarrow}$}), only one of which may undergo transition to the excited state $\ket{e}$. Upon pumping the \mbox{$\ket{\!\downarrow}\to\ket{e}$} transition with a $\pi$-pulse, a relaxation back to the ground state maps the logical qubit value to photon-number.} \label{fig:lambda_atom}
\end{figure}

@@

\begin{figure}[!htbp]
\includegraphics[width=0.225\textwidth]{atomic_ensemble_qubit}
\captionspacefig \caption{Coupling a polarisation-encoded photonic qubit to a pair of atomic ensembles, each of which corresponds to one of the qubit's logical basis states ($\ket{0}$ or $\ket{1}$). The horizontal and vertical components of the photonic qubit are spatially separated using a PBS, which subsequently independently interface with distinct atomic ensembles via collective excitation.} \label{fig:atomic_ensemble_qubit}
\end{figure}

>>>>

For example, the cost metrics and attributes employed at the intercontinental level would most certainly be very different to those in a small LAN. A small LAN might be running applications whereby they can easily reproduce packets and thereby tolerate packet loss. But for a warehouse-scale commercial quantum computing enterprise, responsible for performing one stage of a distributed quantum computation, the loss of a single packet could be extremely costly, requiring the entire computation to be performed completely from scratch due to no-cloning\index{No-cloning theorem} and no-measurement limitations, something that may not come cheaply.

@@

\begin{figure}[!htbp]
\includegraphics[clip=true, width=0.3\textwidth]{opt_inter}
\captionspacefig \caption{Light-matter interfacing between a single-photon state ($\hat{a}$, $\hat{a}^\dag$) and a two-level matter qubit ($\ket{g}$, $\ket{e}$). The absorption (emission) of a photon is associated with the excitation (relaxation) of the matter qubit ($\hat\sigma^\pm$).} \label{fig:opt_int}
\end{figure}

@@

\begin{figure}[!htbp]
\includegraphics[clip=true, width=0.225\textwidth]{lambda_atom}
\captionspacefig \caption{Light-matter interfacing between an optical mode and a $\lambda$-configuration system. The two degenerate ground states represent the logical qubit (\mbox{$\ket{0}_L\equiv\ket{\!\uparrow}$}, \mbox{$\ket{1}_L\equiv\ket{\!\downarrow}$}), only one of which may undergo transition to the excited state $\ket{e}$. Upon pumping the \mbox{$\ket{\!\downarrow}\to\ket{e}$} transition with a $\pi$-pulse, a relaxation back to the ground state maps the logical qubit value to photon-number.} \label{fig:lambda_atom}
\end{figure}

@@

\begin{figure}[!htbp]
\includegraphics[clip=true, width=0.225\textwidth]{atomic_ensemble_qubit}
\captionspacefig \caption{Coupling a polarisation-encoded photonic qubit to a pair of atomic ensembles, each of which corresponds to one of the qubit's logical basis states ($\ket{0}$ or $\ket{1}$). The horizontal and vertical components of the photonic qubit are spatially separated using a PBS, which subsequently independently interface with distinct atomic ensembles via collective excitation.} \label{fig:atomic_ensemble_qubit}
\end{figure}
